\section{Introduction}
\label{sec:introduction}

\LaTeX{} is the standard document preparation system for academic and scientific
publishing. Originally created by Leslie Lamport as a set of macros on top of
Donald Knuth's \TeX{} typesetting engine, it has become indispensable for
producing high-quality technical documents.

\subsection{Why \LaTeX{}?}

There are several compelling reasons to use \LaTeX{} over conventional
word processors:

\begin{itemize}
  \item \textbf{Mathematical typesetting} --- unmatched precision and beauty
    for equations, from simple inline expressions like $E = mc^2$ to complex
    multi-line derivations.
  \item \textbf{Consistent formatting} --- separation of content and
    presentation ensures uniform styling throughout the document.
  \item \textbf{Cross-referencing} --- automatic numbering of sections,
    equations, figures, and tables with reliable cross-references.
  \item \textbf{Bibliography management} --- seamless integration with
    Bib\TeX{} for citation handling.
  \item \textbf{Version control} --- plain text source files work naturally
    with Git and other version control systems.
\end{itemize}

\subsection{About This Project}

This file (\texttt{introduction.tex}) is included via the \verb|\input{}|
command in \texttt{main.tex}, demonstrating multi-file project support.
You can split large documents across multiple files for better organization.

Try editing this section and recompiling to see your changes reflected in the
PDF preview on the right.
