\documentclass[11pt, a4paper]{article}

\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{amsmath, amssymb, amsthm}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage{booktabs}
\usepackage{geometry}
\usepackage{lmodern}

\geometry{margin=1in}

\hypersetup{
  colorlinks=true,
  linkcolor=blue,
  citecolor=blue,
  urlcolor=blue
}

\newtheorem{theorem}{Theorem}
\newtheorem{lemma}[theorem]{Lemma}

\title{Exploring the Foundations of Mathematical Analysis}
\author{cc-latex Demo Project}
\date{\today}

\begin{document}

\maketitle

\begin{abstract}
This document demonstrates the capabilities of the cc-latex IDE, including
multi-file projects, mathematical typesetting, tables, cross-references,
and bibliography management. Edit any file in the tree on the left, or ask
the AI assistant below for help writing your next paper.
\end{abstract}

\tableofcontents

\input{introduction}

\section{Mathematical Typesetting}

One of \LaTeX's greatest strengths is its ability to render complex mathematics
with precision and clarity.

\subsection{Equations}

The Euler--Lagrange equation governs the calculus of variations:
\begin{equation}
  \frac{\partial \mathcal{L}}{\partial q} - \frac{d}{dt}\frac{\partial \mathcal{L}}{\partial \dot{q}} = 0
  \label{eq:euler-lagrange}
\end{equation}

A particularly elegant identity connects five fundamental constants:
\begin{equation}
  e^{i\pi} + 1 = 0
  \label{eq:euler}
\end{equation}

\subsection{Theorems}

\begin{theorem}[Fundamental Theorem of Calculus]
  Let $f$ be a continuous function on $[a, b]$ and let $F$ be an antiderivative
  of $f$. Then
  \[
    \int_a^b f(x) \, dx = F(b) - F(a).
  \]
\end{theorem}

\begin{lemma}
  For any $n \times n$ matrix $A$,
  \[
    \det(A^T) = \det(A).
  \]
\end{lemma}

\subsection{Aligned Equations}

Maxwell's equations in differential form:
\begin{align}
  \nabla \cdot \mathbf{E}  &= \frac{\rho}{\varepsilon_0}          \label{eq:gauss} \\
  \nabla \cdot \mathbf{B}  &= 0                                    \label{eq:gauss-mag} \\
  \nabla \times \mathbf{E} &= -\frac{\partial \mathbf{B}}{\partial t} \label{eq:faraday} \\
  \nabla \times \mathbf{B} &= \mu_0 \mathbf{J} + \mu_0 \varepsilon_0 \frac{\partial \mathbf{E}}{\partial t} \label{eq:ampere}
\end{align}

\section{Tables and Figures}

Table~\ref{tab:complexity} summarizes the time complexity of common sorting algorithms.

\begin{table}[ht]
  \centering
  \caption{Comparison of sorting algorithm complexities}
  \label{tab:complexity}
  \begin{tabular}{@{} l c c c @{}}
    \toprule
    Algorithm      & Best Case        & Average Case     & Worst Case       \\
    \midrule
    Merge Sort     & $O(n \log n)$    & $O(n \log n)$    & $O(n \log n)$    \\
    Quick Sort     & $O(n \log n)$    & $O(n \log n)$    & $O(n^2)$         \\
    Heap Sort      & $O(n \log n)$    & $O(n \log n)$    & $O(n \log n)$    \\
    Insertion Sort & $O(n)$           & $O(n^2)$         & $O(n^2)$         \\
    Bubble Sort    & $O(n)$           & $O(n^2)$         & $O(n^2)$         \\
    \bottomrule
  \end{tabular}
\end{table}

\section{Cross-References}

As shown in Equation~\ref{eq:euler-lagrange}, variational principles are
foundational in physics. Gauss's law (Equation~\ref{eq:gauss}) is the first
of Maxwell's equations. The sorting complexities in Table~\ref{tab:complexity}
highlight the efficiency of divide-and-conquer approaches.

\section{Conclusion}

This demo project showcases multi-file \LaTeX{} editing with cc-latex.
Try editing this file or \texttt{introduction.tex}, then compile with
\textbf{Ctrl+Shift+B} to see the result. Use the AI chat below for help
writing, formatting, or debugging your documents.

For more on \LaTeX{} best practices, see Knuth~\cite{knuth1984} and
Lamport~\cite{lamport1994}. Online resources like the Overleaf
documentation~\cite{overleaf2024} are also excellent references.

\bibliographystyle{plain}
\bibliography{references}

\end{document}
